Generate data for NOBA cod ensemble modeling

### 2020-03-20 NOBAcod.Rmd
test plots for NOBA from standard outputs

```{r full-test, eval=FALSE}

@@

Natageplot <- ggplot(Natagesubsp, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          sp))

  Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 1, scales="free")
  Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 2, scales="free")
  Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 3, scales="free")
  Natageplot + facet_wrap_paginate(~time, ncol=3, nrow = 3, page = 4, scales="free")
```

@@

>>>>

```{r full-test}

@@

Natage <- filter(age_comp_data, time %in% c(55:175))

Natageplot <- ggplot(Natage, aes(x=agecl, y=atoutput)) +
    geom_point() +
    theme_tufte() +
    labs(subtitle = paste(scenario.name,
                          Natage$species))

  Natageplot + facet_wrap(~time/stepperyr, ncol=6, scales="free_y")
```

@@

NEXT!!
